---
title: "Group 5 - Binary Logistic Regression"
author: "Akash Mittal; Antonella, Xaver"
date: "2024-06-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading the dataset
```{r}
library(readr)

Test <- read_csv("C:/Users/Akash Mittal/Documents/GitHub/BayesianAnalysis/Assessment/Group_5/Test.csv")

```

```{r}
df <- Test
str(df)

df$senility <- as.factor(df$senility)
```

```{r}
library(ggplot2)

# Plot of Number of Elderly People in Wais Categories
plot1 <- ggplot(data=Test, aes(x=wais,fill=as.factor(wais))) + labs(x = "Wais Score" , y = "Number of Elderly People", title = "Frequency Distribution of Elderly People")
rainbow_colors <- rainbow(20)
# Print the Plot
plot1 + geom_bar() + scale_fill_manual(values = rainbow_colors) + theme_minimal() + theme(plot.title = element_text(hjust = 0.5)) + theme(legend.position = "none")


# Plot of Number of Elderly People in Wais Categories
plot2 <- ggplot(data=Test, aes(x=senility, fill=senility)) + labs(x = "Senility" , y = "Number of Elderly People" , title = "Frequency Distribution of Elderly People vs Senility", fill = "Senility")

plot2 + geom_bar() + scale_fill_manual(values = c("Yes" = "lightblue2", "No" = "lightgreen")) + theme_minimal() + theme(plot.title = element_text(hjust = 0.5))


# Box Plot for Distribution of Elderly People

ggplot(data=Test, aes(x=senility, y=wais, fill = senility)) +
  geom_boxplot(varwidth = TRUE) + scale_fill_manual(values = c("Yes" = "lightblue2", "No" = "lightgreen")) +
  labs(x="Senility", y="Number of Elderly People", title = "Box Plot for Distribution of Elderly People", fill = "Senility") +
  stat_summary(fun = mean,
               color = "darkblue",
               geom = "point",
               shape = 4,
               size = 4,
               show.legend = FALSE) +
  stat_summary(fun = mean, 
               colour = "darkblue", 
               geom = "text", 
               show.legend = FALSE, 
               vjust = -1.2, 
               aes(label = round(after_stat(y), digits = 3))) +
  theme_minimal() + theme(plot.title = element_text(hjust = 0.5))

```

##### Creating a new Variable for category of WAIS Scores
##### The following are commonly used diagnostic labels together with corresponding numerical limits in terms of IQs and percentages.
##### IQ	Classification
##### 130 and above	Very Superior
##### 120-129	Superior
##### 110-119	High Average
##### 90-109	Average
##### 80-89	Low Average
##### 70-79	Borderline
##### 69 and below	Mentally Retarded

```{r}

Test$wais_category <- cut(Test$wais,
#                          breaks = c(0,69,79,89,109,119,129,Inf),
                           breaks = c(0, 6, 10, 14, 18, Inf),
                           labels = c("Very Low", "Low", "Below Average", "Average", "Above Average"),
                          right = FALSE)


str(Test)
```
##### Barplot of Distribution of categories
```{r}

ggplot(data = Test, aes(x = wais_category, fill = senility)) +
  labs(x = "Wais Category", y = "Count of Elderly People", title = "Distribution of Elderly People in Wais Categories", fill = "Senility") +
  geom_bar() + scale_fill_manual(values = c("Yes" = "lightblue2", "No" = "lightgreen")) +
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5))

```
##### Fitting the Binary Logistic Model (No Square Terms)

```{r}

m_senility <- glm(df$senility ~ df$wais, data=df, family=binomial(link="logit"))

summary(m_senility)

library(MASS)

confint(m_senility)


```

##### Model with Square Terms - [I(df$wais^2)]

```{r}

m_senility1 <- glm(df$senility ~ df$wais + I(df$wais^2), data=df, family=binomial(link="logit"))

summary(m_senility1)

confint(m_senility1)

```


##### Comparing AIC(Akaike Information Criterion) values of the two models

```{r}

aic_small_model <- AIC(m_senility)
aic_large_model <-AIC(m_senility1)

cat("AIC of Small Model : ", aic_small_model,"\n")
cat("AIC of Large Model : ", aic_large_model)
```
##### We see that AIC of small model (m_senility) is less than that of large model (m_senility1), so we finally choose the smaller model.

##### Also calculating the Deviance for the two models.

```{r}

deviance_small_model = pchisq(deviance(m_senility), # Specify the model under consideration
       df.residual(m_senility), # Specify the model under consideration
       lower = FALSE)


deviance_large_model = pchisq(deviance(m_senility1), # Specify the model under consideration
       df.residual(m_senility1), # Specify the model under consideration
       lower = FALSE)

cat("Deviance of Small Model : ",deviance_small_model,"\n")
cat("Deviance of Large Model : ",deviance_large_model,"\n")

```

##### Test Anova for the two models

```{r}
## Performing Anova on the two models

anova_results <- anova(m_senility, m_senility1,test = "Chisq")

cat("ANOVA Table:\n")
anova_results

```

##### Since p-value is greater than 0.05, we do not reject the Null-Hypothesis, and conclude that the small model is better than the Large Model.
##### Further, we note that the Confidence Interval doesn't include the 0.






































































